\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Ayushmaan Singh} % Your name
% You can merge both of these into a single line, if you do not have a website. 
\address{\href{mailto:s.ayushmaan06@gmail.com}{s.ayushmaan06@gmail.com} \\ \href{https://www.linkedin.com/in/ayushmaan03}{linkedin.com/in/ayushmaan03} \\ 
%\href{https://www.username.in/}{YourPortfolio.in} \\ 
\href{https://github.com/Ayushmaan06}{Github} \\ 
\href{tel:9122363999}{Phone-Number}}  %

\begin{document}


%\begin{rSection}{Career Overview}

%A motivated and results-driven Computer Science student with a %strong foundation in Python development, data structures, and %algorithms. Experienced in building scalable applications and %automation systems, with a proven track record of improving %efficiency by 50\% in a professional setting. Seeking to leverage %my technical skills and problem-solving abilities in a challenging %software development role.

%\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Indian Institute of Information Technology, Nagpur, India} \hfill {2023 - 2027}

 Bachelor of Technology, Computer Science \& Engineering \hfill \textit{CGPA : 9.38}
%{\bf AISSCE (Class XII)}, Delhi Public School, Bokaro, India \hfill {2016 - 2018} \\
%Aggregate: 90.5\%

\end{rSection}

%----------------------------------------------------------------------------------------
% TECHINICAL STRENGTHS	
%----------------------------------------------------------------------------------------


\begin{rSection}{EXPERIENCE}
\textbf{Software Development Engineer - Intern } \hfill Oct 2024 - Present\\
\textbf{\href{https://www.linkedin.com/company/infosys-springboard/}{Infosys Springboard}}   \hfill \textit{Remote}
 \begin{itemize}
    \itemsep -3pt {} 
     \item Reduced manual effort in data gathering by 90\% through a Python-based scraper that retrieves and organizes up-to-date deal information.
     \item Achieved 3x faster data extraction, allowing users to access accurate deal information for informed purchasing decisions within seconds.
 \end{itemize}
\textbf{Python Developer - Intern } \hfill July 2024 - August 2024\\
\textbf{\href{https://www.linkedin.com/company/navinfotech/}{Navodita Infotech}}   \hfill \textit{Remote}
 \begin{itemize}
    \itemsep -3pt {} 
     \item Engineered an automated system in Python, cutting manual tasks by over 50\% and boosting efficiency by 20\%. 
     \item Accelerated scripts and processes, achieving a 30\% reduction in runtime and resource consumption.
     \item Partnered with cross-functional teams of 5 to define requirements, ensuring the automation system aligns with business objectives.
     
 \end{itemize}



\end{rSection} 

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Projects}

\textbf{MedBoy }  \hfill \
\textbf{\href{https://github.com/Ayushmaan06/MedBoy}{Git}}   
 \begin{itemize}
    \itemsep -3pt {} 
     \item Architected a specialized language model (LLM) trained over 10,000 medical records for healthcare, processing and accurately answering over 5,000 medical queries daily with a 95\% accuracy rate.
 \end{itemize}

\textbf{e-commerce price tracker }  \hfill \
\textbf{\href{https://github.com/Ayushmaan06/e-commerce-price-tracker}{Git}}   
 \begin{itemize}
    \itemsep -3pt {} 
     \item Built a Python-based price tracking system, monitoring over 10,000 products in real-time across e-commerce platforms, boosting user savings by 20\% through timely price drop alerts.
 \end{itemize}

\textbf{UpSolve LeetCode }  \hfill \
\textbf{\href{https://github.com/Ayushmaan06/Upsolve-Leetcode}{Git}}   
 \begin{itemize}
    \itemsep -3pt {} 
     \item Engineered a robust web application used by over 250 users, focused on upsolving historical LeetCode contests, and improved user performance by 20\%.
 \end{itemize}
\end{rSection} 


%----------------------------------------------------------------------------------------

\begin{rSection}{SKILLS}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Technologies/Frameworks & HTML, CSS, Tailwind, MongoDB, SQL,  
\\
Developer Tools & VS Code, PyCharm, Git, Linux, GCP, Docker(Familiar)\\
Programming Languages & C++, Javascript, C, Python\\
Machine Learning & Scikit-Learn, TensorFlow, Keras, Pandas, NumPy, BeautifulSoup \\
\end{tabular}\\
\end{rSection}

%----------------------------------------------------------------------------------------
\begin{rSection}{Position of Responsibilities} 
\begin{itemize}
    \itemsep -3pt {} 
     \item Mentor at GirlScript Summer of Code.
      \item Contributed to 3 major open-source programs: Summer of Bitcoin, GirlScript Summer of Code, and Winter of Blockchain.
     \item Core Member of Dot Slash, a CP-DSA club.
     \item Organized Analytica: A datascience Hackathon.
     \item Organized EnigmaXplore: A CTF Event.
     \item Environmental Advocate at Tarumitra (Friends of Trees).
     \item IT Educator at Viklang Vidyalaya.
 \end{itemize}
\end{rSection}
\begin{rSection}{Coding Profiles}

\begin{itemize}
    \item CodeChef: 4-star (Max Rating: 1948), Codeforces: Specialist (Rating: 1448), LeetCode: 430+ problems solved
\end{itemize}

\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}